HyperLogLog: Exponentially Bad in Adversarial Settings

### 2021-05-03 docs/HLL_exp_bad/main.tex
removing draft flag  and adding submission number

\documentclass[sigconf, anonymous, dvipsnames, draft]{acmart} %dvipsnames for old/new macros

\fancyhf{} % Remove fancy page headers 
\fancyhead[C]{Anonymous submission \#9999 to ACM CCS 2021} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

>>>>

\documentclass[sigconf, anonymous, dvipsnames]{acmart} %dvipsnames for old/new macros

\fancyhf{} % Remove fancy page headers 
\fancyhead[C]{Anonymous submission \#147 to ACM CCS 2021} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}
